%-------------------------
% Resume in Latex
% Author : Vinayakk Garg
% Adapted from: Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}


\usepackage[charter]{mathdesign} % Bitstream Charter
% \usepackage{newpxtext,newpxmath} % Palatino

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBullet}[2]{
  \item[]\small{
    \hspace{-9pt}\textbf{#1}{: #2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & #2 \\
      \hspace{-10pt}\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% custom commands
\newcommand{\shorterSection}[1]{\vspace{-10pt}\section{#1}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\huge Vinayakk Garg} & Email : \href{mailto:vinayakk.garg99@gmail.com}{\color{blue}vinayakk.garg99@gmail.com}\\
  \href{https://github.com/vinayakkgarg}{\color{blue}github.com/vinayakkgarg} & Mobile : +91-9871838880 \\\\
\end{tabular*}

%-----------EDUCATION-----------------
\shorterSection{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bharati Vidyapeeth's College of Engineering (GGSIPU) }{New Delhi, India}
      {Bachelor of Technology in Information Technology;  GPA: 8.3/10.0}{Expected May 2021}{
      \resumeItemNoBullet{Relevant Coursework}{Introduction to Programming, Data Structures using C, Database Management Systems, Switching theory \& Logic Design, Computer Organisation \& Architecture, Object Oriented Programming using C++}
    }
    \resumeSubheading
      {Montfort Sr. Sec. School}{New Delhi, India}
      {PCM, Computer Science; Percentage: 94.2 }{April 2003 - May 2017}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\shorterSection{Skills}
  \resumeSubHeadingListStart
  \small
    \item{
     \textbf{Languages}{: Python, C, C++, HTML,  CSS, JavaScript}
     \hfill
     \textbf{Technologies}{: Arduino, Raspberry Pi, Git, GitHub, ROS}
    }
    \vspace{-5pt}
    \item{
     \textbf{Libraries}{: Flask, TensorFlow, Keras, Scikit-Learn, Numpy, Pandas, Jupyter, OpenCV, Matplotlib, TKinter}
    }
\resumeSubHeadingListEnd

%-----------PROFESSIONAL EXPERIENCE-----------------
\shorterSection{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SUEZ India}{New Delhi, India}
      {Software  Development Intern}{June 2019 - Present}
      \resumeItemListStart
        \resumeItem{Talking Network}
          {A utility tool to facilitate studying of pipeline diagrams by using voice feedback about parameters of pipelines.
          \begin{itemize}
              \item Worked on a utility tool to promote usability and make readability of blueprint of pipeline networks easier.
              \item Used Google Voice API to do text-to-speech conversion and fetched dynamically changing data in an Android App from a central server. 
          \end{itemize}
          }
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\shorterSection{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/vinayakkgarg/ROS_PacBOT}{\color{blue}ROS\_PacBOT (ongoing)}}
      {A Project developed using the Robotics Operating System. The bots are simulated using the Gazebo Simulator and trained to play the Pacman game using Reinforcement Learning techniques.}
    \resumeSubItem{\href{https://github.com/parulagg27/CraSOS}{\color{blue}CraSOS}}
      {CraSOS is a standalone device with the capabilities of accident prevention, detection and recovery. 
        \vspace{-5pt}
        \begin{itemize}
            \item Rider Rating on basis of speed of riding, braking intensity etc.
            \item Camera on helmet used to click pictures of overspeeding and oddly behaving cars and their number plates.
            \item On collision detection, SOS message(containing location, medical info) generated and sent to helpline numbers and 3 chosen emergency contact numbers.
            \item Information broadcasted using BLE Beacon \& nearby notifications to call for all help possible.
        \end{itemize}
      }
    \resumeSubItem{Real Time Object Detection}
      {Real time all as well as custom object detction on live feed from a USB webcam achieving 15-20 fps.}
    \resumeSubItem{\href{https://github.com/vinayakkgarg/whos-cuter}{\color{blue}Who's Cuter}}
      {A Cats VS Dogs classifier implemented using CNN from scratch with a test set accuracy of 81\% on a dataset of 8000 training images.}
    \resumeSubItem{\href{https://github.com/vinayakkgarg/Lane-Detection-App}{\color{blue}Lane-Detection-App}}
     {A lane lines detection software to determine drivable areas for autonomous robots.}
  \resumeSubHeadingListEnd


%-----------VOLUNTEER EXPERIENCE-----------------
\shorterSection{Volunteer Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Head, RNIS, Developer Student Clubs by Google Developers - BVP}{New Delhi, India}
      {Robotics and Intelligent Systems}{May 2019 - Present}
      \vspace{-5pt}
        \begin{itemize}[noitemsep]
            \item Heading a team of 10 technical executives and 300 student members
            \item Responsible for organising events and mentor workshops in the field of robotics and machine learning
            \item Organised and Mentored a Hardware Hackathon on Arduino Day 2018 with 40+ participating teams from 8 different colleges
            \item Judged an intra-college Ideathon event with 20+ participating teams.
            
        \end{itemize}
  \resumeSubHeadingListEnd


%-----------Addtional Experience & Achievements-----------------
\shorterSection{Additional Experience \& Achievements}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Finalist: SKYHACK}{August 2018}
      {Qualified for the Finals among the top 5 teams nationally for the
Hackathon organised by the Chhattisgarh Government in Raipur.}{AIC@36Inc}
    \resumeSubheading
      {Third: Hack@BVP 2.0}{October 2018}
      {Secured Third position at BVCOE\rq s Hackathon organised by CSE
department.}{CSE DEPT, BVCOE}
    \resumeSubheading
      {Winner: Technovation at Innerve}{October 2017, 2018}
      {Won the first position at IGDTUW\rq s Techfest in the
Ideathon event for two years consecutively}{IGDTUW}
    \resumeSubheading
      {Second: Ideathon at Innovision}{October 2018}
      {Won the second position at NSUT\rq s Techfest in the
Ideathon event.}{E-Cell, NSUT}
    \resumeSubheading
      {Winner: Robo Soccer}{2017}
      {Won the first position in Robo Soccer at IGDTUW, MSIT, BVCOE, CIC.}{IGDTUW, MSIT, BVCOE, CIC}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}